Fail Faster

### 2025-03-15 paper/paper.tex
skeleton of explanation about pw equivalence

@@

\jwc{Explain effect ordering here!!}

>>>>

\jwc{
Explain effect ordering here!!
\begin{itemize}
  \item \texttt{Bq.bind} has the CBV sampling semantics
  \item If you \texttt{Bq.bind} \texttt{x} and then use it twice, both uses refer to the \emph{same} value.
  \item Sampling is effectful: it mutates the internal state.
  \item Permuting two independent binds gives you a generator that is distributionally equivalent, but not equivlaent when considered up to pointwise equality as \emph{functions} from seed to value.
  \item Note that it's much more sensible to compare the bugfinding performance of two function-equivalent generators:
\end{itemize}
}

@@
